Gaudeamus 2017 Figures

### 2018-01-07 inst/examples/201705-Gaudeamus.Rmd
Added data for HS

```{r Gaudeamus-Suomi2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6, dev="CairoJPEG"}
library(dplyr)
theme_set(theme_bw(22))
df2 <- df.combined.preprocessed
df2$publication_place[!df2$publication_place %in% c("Helsinki", "Turku", "Vaasa")] <- "Muu"
df2 <- df2 %>%
       	       filter(!is.na(publication_decade)) %>% 
       	       filter(catalog == "Fennica") %>%
       	       filter(country == "Finland") %>%
       	       filter(publication_year >= 1640) %>%
       	       filter(publication_year <= 1919) 
p <- ggplot(df2, aes(x = publication_decade)) +
   geom_bar(position = "stack", aes(y = ..count.., fill = publication_place), color = "black") +
   scale_fill_grey() +   
   xlab("Vuosi") +
   ylab("Dokumenttia (n)") +
   scale_x_continuous(breaks = c(1640, 1764, 1809, 1863, 1917),
     	              labels = c(1640, 1764, 1809, 1863, 1917)) +
   guides(fill = guide_legend(keywidth=1, title = "Julkaisupaikka")) +
   theme(legend.position = c(0.16, .7)) 
print(p)
```

>>>>

```{r Gaudeamus-Suomi2, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=6, dev="CairoJPEG"}
library(dplyr)
theme_set(theme_bw(22))
df2 <- df.combined.preprocessed
df2$publication_place[!df2$publication_place %in% c("Helsinki", "Turku", "Vaasa")] <- "Muu"
df2 <- df2 %>%
       	       filter(!is.na(publication_decade)) %>% 
       	       filter(catalog == "Fennica") %>%
       	       filter(country == "Finland") %>%
       	       filter(publication_year >= 1640) %>%
       	       filter(publication_year <= 1919) 
p <- ggplot(df2, aes(x = publication_decade)) +
   geom_bar(position = "stack", aes(y = ..count.., fill = publication_place), color = "black") +
   scale_fill_grey() +   
   xlab("Vuosi") +
   ylab("Dokumenttia (n)") +
   scale_x_continuous(breaks = c(1640, 1764, 1809, 1863, 1917),
     	              labels = c(1640, 1764, 1809, 1863, 1917)) +
   guides(fill = guide_legend(keywidth=1, title = "Julkaisupaikka")) +
   theme(legend.position = c(0.16, .7)) 
print(p)

table_hs <- df2 %>% group_by(publication_decade, publication_place) %>%
                    tally() %>%
		    spread(publication_place, n, fill = 0)
library(openxlsx)		    
openxlsx::write.xlsx(table_hs, file = "Table_HS_20180107.xlsx")
```
